Water resource utilization regimes at a basin scale: transition framework and development traps

### 2020-08-21 tex/main/manuscript.tex
订正了所有正文的图

\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/causes.pdf}
	\caption{
		Causes of water utilization regime shifts: economy growths, efficiency changes, and managements.
		\textbf{A.} Total irrigated area and water consumption per unit of irrigated area.
		\textbf{B.} Gross values added of industry and services, and their water use density (WUI) respectively.
		\textbf{C.} Number of management practices in different periods, including policy and reservoirs.
		\textbf{D.} Constructions' finished time of each new reservoir and their located regions' water use percentages in basin's total water use, at that time. Red ones denote hub reservoirs in the basin, which plays a role in integrated water management. Size of the points indicates their magnitude of water storage capacities. Some important or special reservoirs' name are denoted: (1) Xiaolangdi reservoir and Three Gorge Reservoir were constructed mainly responsible for managing sediments of the Yellow River. (2) Liujia Gorge, Longyang Gorge, were constructed mainly responsible for managing water flood discharge and storage. Therefore, these marked reservoirs are significant for the entire basin, far crucial than regional development.
	}
	\label{fig:Causes}
\end{figure}

>>>>

\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/causes.pdf}
	\caption{
		Causes of water utilization regime shifts: economy growths, efficiency changes, and managements.
		\textbf{A.} Total irrigated area and water consumption per unit of irrigated area.
		\textbf{B.} Gross values added of industry and services, and their water use density (WUI) respectively.
		\textbf{C.} Constructions' finished time of each new reservoir and their located regions' water use percentages in basin's total water use, at that time. Red ones denote hub reservoirs in the basin, which plays a role in integrated water management. Size of the points indicates their magnitude of water storage capacities. Some important or special reservoirs' name are denoted: (1) Xiaolangdi reservoir and Sanmen Reservoir were constructed mainly responsible for managing sediments of the Yellow River. (2) Liujia Gorge, Longyang Gorge, were constructed mainly responsible for managing water flood discharge and storage. Therefore, these marked reservoirs are significant for the entire basin, far crucial than regional development.
	}
	\label{fig:Causes}
\end{figure}
